analysis-pilot

### 2023-08-16 code/analysis-pilot.Rmd
tag excluded games

games <- read_csv(here("data/games.csv"), col_types="ccc")|> mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

#so like a third mismatch, and only a couple off by more than 1
```

# remove columns: numPlayers, sound, activePlayerCount, trialNum, distractor, tangramURLs, response, target, submitted, X_id, repNum, correct, targetNum, stageIds
```{r}
filtered_data <- raw_data %>% 
  select(-numPlayers) %>% 
  select(-sound) %>%  
  select(-activePlayerCount) %>% 
  select(-trialNum) %>% 
  select(-distractor) %>% 
  select(-tangramURLs) %>% 
  select(-response) %>% 
  select(-target) %>% 
  select(-submitted) %>% 
  select(-X_id) %>% 
  select(-repNum) %>% 
  select(-correct) %>% 
  select(-targetNum) %>% 
  select(-stageIds)

@@

#remove NA cells in "time"
```{r}
filtered_data <- filtered_data %>% 
  drop_na(time)

@@

#relocate columns
```{r}
filtered_data <- filtered_data %>% 
  select(createdAt, everything()) %>% 
  relocate(countCorrect, .before = time)

@@

#accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(game) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2))

>>>>

games <- read_csv(here("data/games.csv"), col_types="ccc")|> filter(is.na(exclude)) |>  mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

#so like a third mismatch, and only a couple off by more than 1
```
# Prep accuracy

## remove columns: numPlayers, sound, activePlayerCount, trialNum, distractor, tangramURLs, response, target, submitted, X_id, repNum, correct, targetNum, stageIds
```{r}
filtered_data <- raw_data %>% 
  select(-numPlayers) %>% 
  select(-sound) %>%  
  select(-activePlayerCount) %>% 
  select(-trialNum) %>% 
  select(-distractor) %>% 
  select(-tangramURLs) %>% 
  select(-response) %>% 
  select(-target) %>% 
  select(-submitted) %>% 
  select(-X_id) %>% 
  select(-repNum) %>% 
  select(-correct) %>% 
  select(-targetNum) %>% 
  select(-stageIds)

@@

## remove NA cells in "time"
```{r}
filtered_data <- filtered_data %>% 
  drop_na(time)

@@

## relocate columns
```{r}
filtered_data <- filtered_data %>% 
  select(createdAt, everything()) %>% 
  relocate(countCorrect, .before = time)

@@

# accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(game) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2))
